### 2018-03-26 latex/sc18/plots.tex
added ksweep plot

% set options for grouped bar plot
\newcommand{\breakdownplotoptions}{
	ybar stacked,
	reverse legend,
	bar width=8pt,
	width=9cm, height=3.85cm,
	ylabel={Time (s)}, 
	%y label style={yshift=-.5cm},
	ymin=0,
	symbolic x coords={D1,N1,,D16,N16,,D81,N81,,D256},
	xtick=data,
	legend style={at={(0.5,1.3)},anchor=north},
	legend columns=-1,
	reverse legend
}

>>>>

% set options for grouped bar plot
\newcommand{\breakdownplotoptions}{
	ybar stacked,
	reverse legend,
	bar width=8pt,
	width=9cm, height=3.85cm,
	ylabel={Time (s)}, 
	%y label style={yshift=-.5cm},
	ymin=0,
	symbolic x coords={D1,N1,,D16,N16,,D81,N81,,D256,N256},
	xtick=data,
	legend style={at={(0.5,1.3)},anchor=north},
	legend columns=-1,
	reverse legend
}
